\huge Tor's Usability for Censorship Circumvention

### 2016-10-14 pets2017-paper/pets2017-paper.tex
reorganize paper.

We start by introducing terms (section~\ref{sec:background}) and, 
describing the experimental setup (section~\ref{sec:environments}). 
Then we report of user observations and interviews (section~\ref{sec:qualitative}),
evaluate the current interface (section~\ref{sec:eval}), 
list design principles and interface changes (section~\ref{redesign}),
measure the impact of changes in the quantitative experiment in section~\ref{sec:quantitative}, 
testing measured the impact of the design changes (Section~\ref{sec:quantitative}, and
discuss user behaviors (section~\ref{sec:discussion}).
We end with limitations (section~\ref{sec:limitations}), 
related work (section~\ref{sec:related}), 
future work (section~\ref{sec:future}), and
a conclusion (section~\ref{sec:conclusion}).

We contribute:
\smallskip
\begin{itemize}
\item an evaluation of the current configuration interface
\item a redesigned configuration interface
\item logs of 114 users' connection attempts
\item failure modes seen during connection attempts
\item recommended interface changes
\item alternative bootstrapping approaches
\end{itemize}
We hope that our work helps users circumvent censorship and connect to Tor.

>>>>

We start by introducing terms (section~\ref{sec:background}) and, 
describing the experimental setup (section~\ref{sec:environments}). 
Then we report of user observations and interviews (section~\ref{sec:qualitative}),
list design principles and interface changes (section~\ref{redesign}),
state evaluation criteria for gauging the succcessfulness of an interface (section~\ref{sec:eval}), 
measure the impact of changes in the quantitative experiment in section~\ref{sec:quantitative}, 
testing measured the impact of the design changes (Section~\ref{sec:quantitative}, and
discuss user behaviors (section~\ref{sec:discussion}).
We end with limitations (section~\ref{sec:limitations}), 
related work (section~\ref{sec:related}), 
future work (section~\ref{sec:future}), and
a conclusion (section~\ref{sec:conclusion}).

This paper contributes:
\smallskip
\begin{itemize}
\item an evaluation of the current configuration interface
\item a redesigned configuration interface
\item logs of 114 users' connection attempts
\item failure modes seen during connection attempts
\item recommended interface changes
\item alternative bootstrapping approaches
\end{itemize}
We hope that our work helps users circumvent censorship and connect to Tor.
